---
title: "Algal-Dependency in Sub-Tropical, Arid Streams: Tables"
author: "Sean Kinard"
date: "2023-05-24"
output: 
  pdf_document: 
    latex_engine: xelatex
---

```{r , include = F, echo=F, message=F}
setwd('/home/kinard/Documents/Research/Dissertation/03_Autochthony')

library(tidyverse)
library(flextable)
library(knitr)
library(kableExtra)

site_table <- read_csv('Rfig/site_table.csv')
table_aq_assimilated <- read_csv('Rfig/table_aq_assimilated.csv')
table_TL <- read_csv('Rfig/table_TL.csv')
table_siber_range <- read_csv('Rfig/table_siber_and_bstrap_range.csv')
```

\newpage

#### Table 1. Site Characteristics
```{r , echo=F, message=F, warning=FALSE , fig.align = 'center'}
site_table %>% kable(align = c('l', 'c', 'c', 'c', 'c'), digits = 2,
        "latex", booktabs = T, escape=T, table.envir = "center") %>% 
  kable_styling(latex_options = c("solid", "basic", "hold"))
```
Sampling location environmental characteristics (E.variables).
Annual rainfall, annual average temperature and elevation were obtained
from the USGS Gages-ii database. In-situ measurements represent the
seasonal mean $\pm$ the standard error; three measurements were taken every
25 meters within each stream, May-July of 2018, for a total of nine
samples.

\newpage

#### Table 2. Autochthonous Assimilation
```{r , echo=F, message=F, warning=FALSE, fig.align = 'center'}
my_sizes <- c("< 50mm", "< 100mm", "< 150mm", "> 150mm")

table_aq_assimilated %>% 
  filter(! Group %in% my_sizes) %>%
kable(align=c('l','l','l','l'), digits = 2,
        "latex", booktabs = T, escape=T, table.envir = "center" ) %>% 
  kable_styling(latex_options = c("solid", "basic", "hold"))
```
Autochthonous Source assimilation (%) in fish and invertebrate communities, functional feeding groups, and common taxa at Semi-Arid, Transition, and Sub-Humid sites. Values reflect the high density mode and associated 95% credible interval with stars indicating the number of non-overlapping intervals between sites. Autochthonous source assimilation is estimated using $\delta^{13}\text{C}$ and $\delta^{2}\text{H}$ in Bayesian mixing models for each level of comparison (community, feeding group, species/family), calibrated to local aquatic and terrestrial source signatures. 

\newpage

#### Table 3. Isotopic Trophic Level
Isotopic trophic levels for fish and invertebrate
communities as well as functional feeding groups. Each row contains the
group of comparison, the mean $\pm$ the standard deviation, the
sample size (in parentheses) as well as the statistical significance
(whether 95% credible intervals overlap between sites). Sample $\delta^{15}\text{N}$
values were calibrated to the local resources, so isotopic trophic
levels represent the distance from local resources in steps of 3.4‰
$\delta^{15}\text{N}$.

```{r , echo=F, message=F, warning=FALSE, fig.align = 'center'}
table_TL %>% kable(align=c('l','l','l','l'),
        "latex", booktabs = T, escape=T, table.envir = "center" ) %>% 
  kable_styling(latex_options = c("solid", "basic", "hold"))
```

\newpage

#### Table 4. Niche Estimates
Bayesian estimates for the $\delta^{2}\text{H}$ x $\delta^{15}\text{N}$ standard ellipse area and  nearest-neighbor distance, as well as boostrapped estimates of $\delta^{2}\text{H}$ range and $\delta^{15}\text{N}$ range for fish and invertebrate communities. Summary statistics represent the mean and the associated 95% credible interval. Statistical significance stars represent whether one or more pairs of sites have non-overlapping credible intervals.

```{r , echo=F, message=F, warning=FALSE, fig.align = 'center'}
table_siber_range %>% kable(align= c('l', 'l','l', 'l', 'l', 'l'),
        "latex", booktabs = T, escape=T, table.envir = "center" ) %>% 
  kable_styling(latex_options = c("solid", "basic", "hold"))
```


